\huge A Usability Evaluation of Tor Launcher

### 2016-10-31 pets2017-paper/pets2017-paper.tex
small wording tweaks throughout

Bridges are unlisted Tor relays that can serve as an alternative entry node.
Bridges can be simple, unlisted relays. 
But most bridges run a pluggable tranport (referred to as ``transport'' for shorthand) that obfuscates the traffic. 
Most transports disguise traffic to defeat on-the-wire identification, relying on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Some transports route traffic through other services, avoiding the need for a secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks.
Bridges and transports allow a connection to the Tor network when all publicly listed relays and any Tor-looking packets are blocked. Fig.~\ref{fig:bridge-options} shows the bridge and transport options at the time of the study.

@@

In addition to Tor-specific components, a local proxy is required to connect 
in certain managed networks. In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy. (Technically, Tor relays, bridges, and local proxies all allow indirect network connections to other network services and can be considered a proxy.) Fig.~\ref{fig:topology} illustrates the interacting components.

@@

\subsection{State and Corporate Censorship}
State level censors can vary in their thoroughness in censorship, resulting in a variety of ever-changing network conditions. Some block websites with a combination of IP blacklisting and DNS-poisoning while others that employ more sophisticated techniques such as deep packet inspection and protocol detection. In countries that censor services but do not block censorship circumvention tools, any connection to Tor will byass the censorship. In other countries, sophisticated state-level censorship require bridges that run specific tranports that route traffic through other, non-Tor services first. For example, only meek-amazon and meek-azure transports work to bypass China's GFW.

@@

\pquote{P2}{I don't know what any of those [list of bridges] means, or what that [proxy] means at all.}
\pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
\pquote{P\#}{find when Michael said he didn't know if he was E2 or E3!} 
\pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen. I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}
When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).
%The progress bar has a bug that causes it to update only when the level of progress increases.
%If progress bar reaches a 90\% and fails, the next attempt have regressed to 0\% and remain there until the progress surpasses 90\%. Due to this, participants assumed that their subsequent attempts were wrong, even if they were right.
\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
\pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}

\subsection{Where Users Struggled} 
{\color {blue}
LIST `EM! 
}

\begin{figure}[t]
  \centering
    \includegraphics[width=0.5\textwidth]{error.png}
    \caption{An example of a technical error message which our participants did not understand.}
\label{fig:error}
\end{figure}
}

\section{Design Principles and Changes}
\label{sec:design} 
This section discusses how we converted our formative usability testing observations into design changes.

@@

%time to success and version
Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$). That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance. We used a one-tailed Mann--Whitney test because the distribution of completion times were 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned the maximum time of 40 minutes).

@@

%active time and version
Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$). That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance. We used a one-tailed Mann--Whitney test because the distribution of configuration times were also 1) right-censored and 2) non-normal and heavily right tailed, due to being an artifact of completion time.

@@

\section{Recommendations}
\label{recommendations}
We do believe that adopting our design will help save users time when connecting to Tor. But since we did not test our design changes independently, we cannot (and do not) claim the effects each change we made. Some of our changes may have little or negative effect. Additionally, we recognize equivalent (or more impactful!) changes could be made in place of ours. Therefore, we do not recommend specific changes, but offer some suggestions for Tor Launcher's GUI based on what we learned: \\

@@

Although the abovementioned suggestions will improve the deployed interface, we recommend exploring solutions that leverage automation, user-dependent inputs, or network-dependent inputs. We start this discussion by sharing some of our own ideas in appendix~\ref{alternatives}.

>>>>

Bridges are unlisted Tor relays that serve as an alternative entry node.
Bridges can be simple, unlisted relays. 
But most bridges run a pluggable tranport (referred to as ``transport'' for shorthand) that obfuscates the traffic. 
Most transports disguise traffic to defeat on-the-wire identification, relying on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Some transports route traffic through other services, avoiding the need for a secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks.
Bridges and transports allow a connection to the Tor network when all publicly listed relays and any Tor-looking packets are blocked. Fig.~\ref{fig:bridge-options} shows the bridge and transport options at the time of the study.

@@

A local proxy is required to connect 
in certain managed networks. In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy. (Technically, Tor relays, bridges, and local proxies all allow indirect network connections to other network services and can be considered a proxy.) Fig.~\ref{fig:topology} illustrates the interacting components.

@@

\subsection{State and Corporate Censorship}
State level censors can vary in their thoroughness in censorship. Some block websites with a combination of IP blacklisting and DNS-poisoning while others that employ more sophisticated techniques such as deep packet inspection and protocol detection. In countries that censor services but do not block censorship circumvention tools, any connection to Tor will byass the censorship. In other countries, sophisticated state-level censorship require custom bridges or bridges that run specific tranports that route traffic through non-Tor services first.

@@

\pquote{P2}{I don't know what any of those [list of bridges] means, or what that [proxy] means at all.}
\pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
\pquote{P\#}{find when Michael said he didn't know if he was E2 or E3!} 
\pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen. I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}
When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).
%The progress bar has a bug that causes it to update only when the level of progress increases.
%If progress bar reaches a 90\% and fails, the next attempt have regressed to 0\% and remain there until the progress surpasses 90\%. Due to this, participants assumed that their subsequent attempts were wrong, even if they were right.
\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
\pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}
}

\begin{figure}[t]
  \centering
    \includegraphics[width=0.5\textwidth]{error.png}
    \caption{An example of a technical error message which our participants did not understand.}
\label{fig:error}
\end{figure}

\subsection{Pain Points in Tor Launcher} 
{\color {blue}
LIST `EM! 
}

\section{A Design Iteration}
\label{sec:design} 
This section discusses how we converted our formative usability testing observations into design changes.

@@

%time to success and version
Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$). That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance. We used a one-tailed Mann--Whitney test because the distribution of completion times were 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned a time of 40 minutes).

@@

%configuration time and version
Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$). That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance. We used a one-tailed Mann--Whitney test because the distribution of configuration times were also 1) right-censored and 2) non-normal and heavily right tailed, due to being an artifact of completion time.

@@

\section{Recommendations}
\label{recommendations}
We do believe that adopting our design will help save users time when connecting to Tor. But since we did not test our design changes independently, we cannot (and do not) claim the effects each change we made. Therefore, we do not recommend specific changes, but offer some suggestions for Tor Launcher's GUI based on what we learned: \\

@@

We also recommend exploring solutions that leverage automation, user-dependent inputs, or network-dependent inputs. We start this discussion by sharing some of our own ideas in appendix~\ref{alternatives}.
